---
title: "LinearRegressionNNY"
author: "Alex Norris, Khanh Nguyen, Nan Yang"
date: "Date of publish: `r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Linear Regression NNY allows you to perform the general linear regression models from a **independent** and **dependent** variables. It can be utilized for performing regression, t-test, and analysis of covariance. Citation https://smac-group.github.io/ds/section-functions.html#section-example-continued-least-squares-function

## Install package

The package can be installed by following

devtools::install_github("https://github.com/AU-R-Programming/LinearRegressionNNY")

## Load package

```{r load_packge}
library(LinearRegressionNNY)
```

## Getting help

?linear_model

## Usage

linear_model(response, covariates, alpha = 0.05)


## Value
The result from object "linear_model" is a list containing at least the following components:

**beta**: Estimated coefficient, beta hat

**sigma2**: Residuals

**variance_beta**: variance of the beta estimator, beta hat

**ci**: confidence interval, derived from alpha

## Authors

Group 09 and SMAC Group: https://smac-group.github.io/ds/section-functions.html#section-example-continued-least-squares-function.

## Example
```{r use}
data("cars")
linearModel <- linear_model(cars$dist, cars$speed, alpha = 0.05)
summary(linearModel)
```

